---
title: "galah pre-release"
author: "Matilda Stevenson"
date: "1/07/21"
output:
  html_document:
    highlight: default
    toc: true
    toc_float: true
    toc_depth: 3
    # include:
    #   in_header: header.html
    #   after_body: footer.html
    # css: style.css
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "chunk-highlight")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```



------------------------------------------------------------------------------
This document outlines the checks required before submitting `galah` to CRAN.
<br>

------------------------------------------------------------------------------

## Testing

Much of the testing of `galah` is automated, and test coverage is good but there
are still a few things that aren't/can't be covered in automated testing. Test
coverage information is available [here](https://app.codecov.io/gh/AtlasOfLivingAustralia/galah).

### Automated tests
```{r eval=FALSE}
# Run all tests
devtools::test()

# Run individual tests
devtools::test_active_file()
```

### Manual tests
Some examples of things to check are here (this is not an exhaustive list)  

* https://confluence.csiro.au/display/ALASD/galah+and+ALA4R+functional+tests
* International Atlas configuration
* Documentation

### Documentation checks
First, build all the documentation. Hopefully nothing changes when this is run
as it should have been done when documentation was updated.
```{r eval = FALSE}
roxygen2::roxygenise()
```
Then build the `pkgdown` site locally
```{r eval = FALSE}
pkgdown::build_site()
```
<br>

------------------------------------------------------------------------------


## Local checks
Ideally these commands should be run outside RStudio
```{bash eval=FALSE}
# Assuming we are in the galah directory 
cd ..
R CMD build galah
# wait for it to finish
R CMD check galah_1.2.0.tar.gz
## check as CRAN
R CMD check --as-cran galah_1.2.0.tar.gz
```

## External checks
```{r eval = FALSE}
rhub::check_for_cran()
```


### Winbuilder 
Winbuilder is software to check R packages for Windows. To use winbuilder to 
check the package:  

* Find the built and zipped package on your system. It will be in the format
`galah_{version}.tar.gz`. 
* Upload the package to [winbuilder](https://win-builder.r-project.org/upload.aspx)- 
only the first and second sections as `galah` doesn't support versions below 
4.0.0
* Wait for emails to maintainer

### Travis
Travis is Continuous Integration software. It builds and checks the package on
an external server. Checks are run automatically anytime code is pushed to 
GitHub, and the results are visible [here](https://travis-ci.com/AtlasOfLivingAustralia/galah)

## ALA Admin
All software releases must be approved by the Change Advisory Board (CAB).
Change requests are created in JIRA, and approved by various people. It is just
to check that due diligence has been done. Most parts can be copied over from
one release to the next. The change request register can be viewed [here](https://jira-sd.csiro.au/projects/ACRR/queues/custom/367/ACRR-237)
