---
title: "Tracking `galah` usage"
author: "Matilda Stevenson"
date: '`r Sys.Date()`'
output: rmarkdown::html_vignette
---

```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(scales)
library(lubridate)
library(stringr)
```

### Versions of package being used
Excludes CRAN, travis and `ala4r@ala.org.au` email. This data comes from the
server logs stored in Kibana. The user-agent header is used to determine 
which package and which versions of the package are being used.
*Note: `koala` was the temporary name for `galah`.*

```{r include=FALSE}
# Behind the scenes work required to pull the relevant files from AWS S3
library(paws)
# Create an S3 object
s3 <- paws::s3()
# List all files holding Kibana data
bucket_id <- Sys.getenv("AWS_BUCKET_ID")
objs <- s3$list_objects(Bucket = bucket_id, Prefix = "kibana_data")
# Condense the results into a more readable dataframe
obj_df <- data.frame(
  matrix(
    unlist(objs$Contents),
    nrow=length(objs$Contents),
    byrow=TRUE
    )
  )
names(obj_df) <- c("key", "last_modified", "etag", "size", "storage_class")

# Package version data
pkg_version_keys <- obj_df %>%
  filter(grepl("package_versions", key)) %>%
  pull(key)

# Request path data
request_path_keys <- obj_df %>%
  filter(grepl("request_paths", key)) %>%
  pull(key)

# Requests by user-agent data
requests_ua_keys <- obj_df %>%
  filter(grepl("requests_by_ua", key)) %>%
  pull(key)

# Unique users by user-agent data
users_ua_keys <- obj_df %>%
  filter(grepl("unique_users_by_ua", key)) %>%
  pull(key)

# Given a vector of object names, download all the data
get_data <- function(keys) {
  data.table::rbindlist(lapply(keys, function(key) {
    obj <- s3$get_object(
      Bucket = Sys.getenv("AWS_BUCKET_ID"),
      Key = key
      )
    read.csv(text = rawToChar(obj$Body))
  }))
}
```

```{r warning=FALSE, message=FALSE, fig.width=8}
# Merge files from all dates
counts <- get_data(pkg_version_keys)
counts$date <- as.Date(counts$date)

# Request counts over time
ggplot(counts) + geom_point(mapping = aes(x = date, y = doc_count, colour = key)) +
  scale_x_date(date_labels = "%b", date_break = "month")
```

### Number of requests with an email
Excludes CRAN, travis and `ala4r@ala.org.au` email

```{r warning=FALSE, message=FALSE, fig.width=8}
# Merge files from all dates
counts <- get_data(requests_ua_keys)
counts$date <- as.Date(counts$date)
counts <- counts %>% filter(user_agent_class %in% c("ALA4R 1.8.0", "ALA4R 1.9.0",
                                                    "galah 1.0.0", "koala 1.0.0",
                                                    "R", "python", "web-browser"))

# Request counts over time
ggplot(counts) + geom_point(mapping = aes(x = date, y = request_count,
                                         colour = user_agent_class)) +
  scale_x_date(date_labels = "%b", date_break = "month") +
  scale_y_log10()
```

### Number of unique users downloading data with an email
Excludes CRAN, travis and `ala4r@ala.org.au` email
```{r warning=FALSE, message=FALSE, fig.width=8}
# Merge files from all dates
counts <- get_data(users_ua_keys)
counts$date <- as.Date(counts$date)

counts <- counts %>% filter(user_agent_class %in% c("ALA4R 1.8.0", "ALA4R 1.9.0",
                                                    "galah 1.0.0", "koala 1.0.0",
                                                    "R", "python", "web-browser"))

# Request counts over time
ggplot(counts) + geom_point(mapping = aes(x = date, y = unique_users,
                                         colour = user_agent_class)) +
        scale_y_log10() +
        scale_x_date(date_labels = "%b", date_break = "month")
```

### Which endpoints are used by R users
Excludes CRAN, travis and `ala4r@ala.org.au` email
```{r warning=FALSE, message=FALSE, fig.width=8}
# Merge files from all dates
counts <- get_data(request_path_keys)
counts$date <- as.Date(counts$date)

# summarise by type
grouped_counts <- counts %>% group_by(key2, path_type, date) %>%
  summarise(total = sum(doc_count))

# How to visualise this?
```